SVG: The Paper

### 2022-04-12 Analysis/sup_mat.Rmd
Tagu initial selections

>>>>

## Tagu dataset

```{r}
d <- read_csv("data/tagu_2020_prox_mouse.csv", show_col_types = FALSE) %>%
  filter(found == 1) %>%
  mutate(condition = as_factor(condition))

ggplot(d, aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
  #coord_cartesian(xlim = c(0, 1), ylim = c(0, 1)) + 
  facet_wrap(~observer)

d %>% group_by(observer, condition) %>% 
  summarise(x = median(x), y = median(y)) %>%
  ggplot(aes(x, y, colour = condition)) + geom_point(alpha = 0.25) #+
  #coord_cartesian(xlim = c(0, 1), ylim = c(0, 1))
